---
title: "Lab 1: Review"
author: "Public Health Metrics"
date: "January 9, 2017"
output: html_document
---

```{r L1, echo=FALSE, warning=FALSE, message=FALSE}
#The dataset we are exploring has influenza and pneumonia deaths on a state and national level, over time.
#https://www.healthdata.gov/dataset/deaths-pnuemonia-and-influneza-and-all-deaths-state-and-region-national-center-health

#We will be requiring knitr, dplyr, and ggplot2
install.packages("knitr")
install.packages("dplyr")
install.packages("ggplot2")

library(knitr)
library(dplyr)
library(ggplot2)
```

#Read in the dataset
fludata = read.csv("flu_deaths.csv")


#Handle NA values
fludata[is.na(fludata)] <- 0
# set all NA values to zero


#Create one summary table and one plot about two different aspects of the dataset. Include a small paragraph explaining what each table/plot is showing.
The summary table includes information about the different variables, like the minimum value, maximum value, and the quartile values.

Play around with markdown syntax to create *interesting* and **engaging** text.

```{r table, echo=FALSE}
#Summary Table
summary(fludata)
```

```{r plot, echo=FALSE}
#Plot
qplot(fludata$age, fludata$Deaths.from.pneumonia.and.influenza, data=fludata)
```

```{r challenge, echo=FALSE}
#If you are looking for a challenge, try to use the MMWR.Year.Week data to show the number of deaths over time for one season

```

